---
title: "Problem Set 2"
author: "Westley Cook"
date: "2/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(fivethirtyeight)
library(lintr)

# Loading the tidyverse and fivethirtyeight packages because the pset said
# I would need them. Loading lintr because the tidyverse style guide said it
# would perform automated checks to make sure I was conforming to the style
# guide, and I anticipate needing help to not lose points on style issues
# since I've never done this before.

x <- endorsements_2020

# Renaming endorsements_2020 as x so it's easier to call as I work on the
# rest of the pset.
```

```{r madlib_1, include=FALSE}

```


1. The earliest date for an endorsement in the dataset is X

2. The most recent date for an endorsement is X

3. X is the mayor that has endorsed Pete Buttigieg.

4. Endorsers from New Hampshire have an average of X endorsement points.

5. Between them, the two female candidates who remain in the race (Amy Klobuchar and Elizabeth Warren) have a total of X endorsement points.

6a. The variable “position” is a X class of variable.

6b. The variable “endorser” is a X class of variable.

6c. The variable “points” is a X class of variable.