---
title: "Problem Set 2"
author: "Westley Cook"
date: "2/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Loading the tidyverse and fivethirtyeight packages because the pset said I
# would need them. Loading lintr because the tidyverse style guide said it would
# perform automated checks to make sure I was conforming to the style guide, and
# I anticipate needing help to not lose points on style issues since I've never
# done this before *upside-down smiley face*.

library(tidyverse)
library(fivethirtyeight)
library(lintr)

```

```{r exploring_data, include = FALSE}

# Used glimpse(endorsements_2020) and then summary(endorsements_2020) to get a
# sense for what this dataframe looks like.

```

## Mad Libs

```{r madlib_1, include=FALSE}

# This r chunk assigns a variable to insert in-line in mad lib 1.

# Ran the arrange() command to figure out what the earliest date was, then used
# the slice() command to isolate just the first row of the dataframe. Then
# pulled the value from the date column and named it first_date so I could slot
# it in nicely for the Mad Lib.

first_date <- endorsements_2020 %>% 
                arrange(date) %>% 
                slice(1) %>% 
                pull(date)

```

1. The earliest date for an endorsement in the dataset is **`r first_date`**.

```{r madlib_2, include = FALSE}

# This r chunk assigns a variable to insert in-line in mad lib 2.

# Same process as for Mad Lib 1, but adding desc() within the arrange() function
# to reverse the order of the output and give me the most recent date instead of
# the oldest one.

most_recent_date <- endorsements_2020 %>% 
                      arrange(desc(date)) %>% 
                      slice(1) %>% 
                      pull(date)

```

2. The most recent date for an endorsement is **`r most_recent_date`**.

```{r madlib_3, include = FALSE}

# This r chunk assigns a variable to insert in-line in mad lib 3.

# Filtered first by position to narrow the data to only the mayors who have
# given endorsements. Then added the argument endorsee == "Pete Buttigieg" to
# isolate only the one mayor who endorsed him. Used pull() command to grab that
# mayor's name and assign it to the variable "mayor", which I then placed in an
# embedded r in mad lib 3.

mayor <- filter(endorsements_2020, 
                  position == "mayor", 
                  endorsee == "Pete Buttigieg") %>% 
         pull(endorser)

```

3. **`r mayor`** is the mayor that has endorsed Pete Buttigieg.

```{r madlib_4, include = FALSE}

# This r chunk assigns a variable to insert in-line in mad lib 4.

# Set filter(state == "NH") to give just the NH rows, and the first thing I
# tried was to just pipe it into a mean() operation and name the result
# nh_avg_points. But the mean() operation didn't work, because the points date
# type is <dbl>, which apparently doesn't work with mean()... So instead, I
# pulled the points out and named that vector points_from_nh.

points_from_nh <- endorsements_2020 %>% 
                    filter(state == "NH") %>% 
                    pull(points)

# I then used a separate operation to take the mean of the points and name it
# nh_avg_points.

nh_avg_points <- mean(points_from_nh)

```

4. Endorsers from New Hampshire have an average of **`r nh_avg_points`** endorsement points.

```{r madlib_5, include = FALSE}

# This r chunk assigns a variable to insert in-line in mad lib 5.

# Very similar process to mad lib 4. I used the vertical bar in the filter()
# operation to filter for Klobuchar or Warren, then pulled the points and named
# them warren_klobuchar_points.

warren_klobuchar_points <- endorsements_2020 %>% 
                             filter(endorsee == "Amy Klobuchar" | 
                                    endorsee == "Elizabeth Warren") %>% 
                             pull(points)

# I then used the sum() operation to take the total of those points and name it
# warren_klobuchar_points_total.

warren_klobuchar_points_total <- sum(warren_klobuchar_points)

```

5. Between them, the two female candidates who remain in the race (Amy Klobuchar and Elizabeth Warren) have a total of **`r warren_klobuchar_points_total`** endorsement points.

```{r madlib_6_note, include = FALSE}

# This r chunk assigns three variables to insert in-line in parts a-c of mad lib
# 6.

# Part a: piping endorsements_2020 into pull() to isolate the position column as
# an object, then calling the class() function to name the class. Assigning the
# resulting value to a new variable called position_class.

position_class <- endorsements_2020 %>%
                    pull(position) %>%
                    class()

# Part b: same process as with part a, but with endorser (and with new variable
# endorser_class) instead of with position.

endorser_class <- endorsements_2020 %>% 
                    pull(endorser) %>% 
                    class()

# Part c: again, same process as with part a, but with points (and with new
# variable points_class) instead of with position.

points_class <- endorsements_2020 %>% 
                  pull(points) %>% 
                  class()

```

6. a. The variable “position” is a **`r position_class`** class of variable.

   b. The variable “endorser” is a **`r endorser_class`** class of variable.

   c. The variable “points” is a **`r points_class`** class of variable.

## Plot Replication

```{r plot_prep, include = FALSE}

# This r chunk loads the gov.1005.data package, which I need for the congress
# data it contains. It then loads the ggthemes package, which I'll use in
# replicating the format and style of the plot.

library(gov.1005.data)
library(ggthemes)

```


```{r plot, echo = FALSE}

# This r chunk first creates a new tibble, the data from which I'll use in the
# plot I'm replicating. It then creates the plot itself, trying to replicate as
# closely as possible the plot from the fivethirtyeight article.

# To create the tibble, I first piped the existing congress dataframe to a
# filter function, filtering by party is "D" or "R" - there might be an easier
# way to do this? Oh well. I then grouped by year and party, piping the result
# into a summarize() function to pull out the average age for each year by
# party.

avg_congress_ages <- congress %>% 
                       filter(party == "D" | 
                              party == "R") %>% 
                       group_by(year, party) %>% 
                       summarize(avg_age = mean(age)
                    )

# Plotting average congress ages with year on x axis, and average age on y axis,
# coloring by party

ggplot(avg_congress_ages,
  aes(x = year,
      y = avg_age,
      color = party)
  ) +

# Making it a line plot
  
  geom_line() +
  
# Setting scale for x axis, using scale_x_continuous per suggestion of the
# assignment. It'll auto-generate appropriate limits, but I want vertical grid
# lines to appear for years from 1950-2010, so I'll use the breaks argument with
# a seq() command to set the first and last years they'll appear, and how much
# space to put between them (by = 10).
  
  scale_x_continuous(breaks = seq(1950,
                                  2010,
                                  by = 10),
                     
# Labeling each of the vertical grid lines, taking label names from the plot I'm
# replicating and using c() to combine them into a character vector.
                     
                     labels = c("1950",
                                "'60",
                                "'70",
                                "'80",
                                "'90",
                                "2000",
                                "'10")
                     ) +
  
# Now will similarly scale and label the y axis, using scale_y_continuous per
# suggestion of the assignment. Unlike the x axis, for this one I need to set
# clear limits (the auto-generated limits don't match the plot I'm replicating).
  
  scale_y_continuous(limits = c(40,
                                62),
                     
# Now setting breaks, like I did for the x axis, but with (obviously) different
# values, copied from the plot I'm replicating.
                     
                     breaks = seq(40,
                                  60,
                                  by = 5),

# Now labeling the y axis as I did with the x axis. Values in the c() operator
# come from the plot I'm replicating.

                     labels = c("40",
                                "45",
                                "50",
                                "55",
                                "60 yrs")
                     ) +
  
# Using the theme_fivethirtyeight() operation to change the background color and
# font and other aspects of the style of the plot; much easier than keying in
# all those changes individually.
  
  theme_fivethirtyeight() + 
  
# Want to add title, subtitle, and caption; using labs() because 1) the
# assignment suggested it, and 2) I can add all the necessary elements within
# this one operation using lab() arguments. Character strings for title,
# subtitle, and caption all copied from the plot I'm replicating; labels are
# NULL because the plot didn't have any.
  
  labs(title = "Average Age of Members of Congress",
       subtitle = "At start of term, 1947-2013",
       labels = NULL,
       caption = "Source: fivethirtyeight package") +
  
# Getting rid of the legend
  
  theme(legend.position = "none") +
  
# Adding text on the plot to insert "Democrats" in blue. Using annotate() per
# suggestion of the assignment. x and y are the coordinates on the plot (figured
# out what the exact numbers should be for those, and for size, through trial
# and error). Other arguments are self-explanatory.
  
  annotate("text",
           x = 1996,
           y = 58,
           label = "Democrats",
           color = "blue",
           size = 5.5) +
  
# Adding text to insert "Republicans" in red, using the same process as I used
# above for "Democrats".
  
  annotate("text",
           x = 1967, 
           y = 57, 
           label = "Republicans",
           color = "red",
           size = 5.5) +
  
# Using scale_color_manual() per suggestion of the assignment to manually change
# the color of the lines on the plot from their default settings, so the
# Democrat line will be blue and the Republican line will be red.
  
  scale_color_manual(values = c("blue",
                                "red")
                     )

```

### Worked with:
Owen Bernstein
- Lindsey Greenhill
- Katelyn Li

###### at Evelyn's Study Hall in Lowell on Tuesday, February 11.